Longitudinal missing tie prediction: Comparing Facebook Networks at the Two Waves
========================================================


Three questions that have been identified:     

1.  How much turnover there is in the observed ties (no imputation is necessary)?
This question can be answered for the respondent-only FB networks at the two time points, and
the respondents + nonrespondents who are friends with 10% of the respondents.

2.	How much turnover there is in the unobserved ties (with cross-sectional imputation at the two waves)?
As stated, this question might not be answerable. 

3.	Which PCAs are persistently selected?
We can conduct an analysis identical to the first paper with the second wave of data, and compare which PCAs are selected both times.

## Comparison of Respondent-Only Networks
```{r, echo=FALSE}
suppressPackageStartupMessages(library(igraph))
load("r0_nets_comparison.RData")
```

In Wave 1, the respondent-only network consisted of `r vcount(w1.resp.ig)` nodes and `r ecount(w1.resp.ig)` edges, indicating a mean degree of 
`r round(2*ecount(w1.resp.ig)/vcount(w1.resp.ig), 1)`. In Wave 2, the corresponding statistics are `r vcount(w2.resp.ig)` and `r ecount(w2.resp.ig)` respectively, with a mean degree of `r round(2*ecount(w2.resp.ig)/vcount(w2.resp.ig), 1)`.  

There are `r nrow(el_rbind[duplicated(el_rbind), ,drop = FALSE])` ties from Wave 1 that also exist in Wave 2. This result implies that 
`r ecount(w2.resp.ig) - nrow(el_rbind[duplicated(el_rbind), ,drop = FALSE])`
ties were seen in Wave 2 but not in Wave 1.

## Comparison of Respondent-Only Networks, restricted to common nodes
```{r, echo=FALSE}
suppressPackageStartupMessages(library(igraph))
load("r0_nets_obtain_com_respondents_w_svy_data.RData")
```

There were `r vcount(w1_com_resp_ig_w_w2svydata)` nodes in waves 1 and 2, who also gave in-person survey data. In Wave 1, these individuals had `r ecount(w1_com_resp_ig_w_w2svydata)` edges, and in Wave 2, they shared `r ecount(w2_com_resp_ig_wsvydata)` edges.   





