## Visualize intersection between different metrics on the raw networks

### Libaraies and Data
```{r, echo=FALSE}

rm(list=ls())

library(ggplot2)
load("../../control-net/control-net-ovelap.RData")
```

###Data

##### All PCA's
```{r, echo=FALSE}
## data
norm_btwn_evcent <- btwn_evcent/length(btwn_885nodes)
norm_btwn_bridging <- btwn_bridging/length(btwn_885nodes)
norm_btwn_kp <- btwn_kp/length(btwn_885nodes)

norm_evcent_btwn <- btwn_evcent/length(evcent_885nodes)
norm_evcent_bridging <- evcent_bridging/length(evcent_885nodes)
norm_evcent_kp <- evcent_kp/length(evcent_885nodes)

norm_bridging_btwn <- btwn_bridging/length(bridging_885nodes)
norm_bridging_evcent <- evcent_bridging/length(bridging_885nodes)
norm_bridging_kp <- bridging_kp/length(bridging_885nodes)

norm_kp_btwn <- btwn_kp/length(kp_885nodes_set300)
norm_kp_evcent <- evcent_kp/length(kp_885nodes_set300)
norm_kp_bridging <- bridging_kp/length(kp_885nodes_set300)
```

```{r, echo=FALSE}
## form matrix
   control_overlap_matrix <- as.data.frame(matrix(1, nrow=4, ncol=4))
   control_overlap_matrix[1, 2:4] <- c(norm_btwn_evcent, norm_btwn_bridging, norm_btwn_kp)
   control_overlap_matrix[2, c(1,3:4)] <- c(norm_evcent_btwn, norm_evcent_bridging, 
                                            norm_evcent_kp)
   control_overlap_matrix[3, c(1,2, 4)] <- c(norm_bridging_btwn, norm_bridging_evcent,
                                             norm_bridging_kp)
   control_overlap_matrix[4, c(1:3)] <- c(norm_kp_btwn, norm_kp_evcent,
                                             norm_kp_bridging)

## view matrix
   control_overlap_matrix
```

##### Respondents selected as PCA's
```{r, echo=FALSE}  
## data
resp_norm_btwn_evcent <- resp_btwn_evcent/length(resp_btwn_885nodes)
resp_norm_btwn_bridging <- resp_btwn_bridging/length(resp_btwn_885nodes)
resp_norm_btwn_kp <- resp_btwn_kp/length(resp_btwn_885nodes)

resp_norm_evcent_btwn <- resp_btwn_evcent/length(resp_evcent_885nodes)
resp_norm_evcent_bridging <- resp_evcent_bridging/length(resp_evcent_885nodes)
resp_norm_evcent_kp <- resp_evcent_kp/length(resp_evcent_885nodes)

resp_norm_bridging_btwn <- resp_btwn_bridging/length(resp_bridging_885nodes)
resp_norm_bridging_evcent <- resp_evcent_bridging/length(resp_bridging_885nodes)
resp_norm_bridging_kp <- resp_bridging_kp/length(resp_bridging_885nodes)

resp_norm_kp_btwn <- resp_btwn_kp/length(resp_kp_885nodes)
resp_norm_kp_evcent <- resp_evcent_kp/length(resp_kp_885nodes)
resp_norm_kp_bridging <- resp_bridging_kp/length(resp_kp_885nodes)


## form matrix
   resp_control_overlap_matrix <- as.data.frame(matrix(1, nrow=4, ncol=4))
   resp_control_overlap_matrix[1, 2:4] <- c(resp_norm_btwn_evcent, resp_norm_btwn_bridging, resp_norm_btwn_kp)
   resp_control_overlap_matrix[2, c(1,3:4)] <- c(resp_norm_evcent_btwn, resp_norm_evcent_bridging, 
                                            resp_norm_evcent_kp)
   resp_control_overlap_matrix[3, c(1,2, 4)] <- c(resp_norm_bridging_btwn, resp_norm_bridging_evcent,
                                             resp_norm_bridging_kp)
   resp_control_overlap_matrix[4, c(1:3)] <- c(resp_norm_kp_btwn, resp_norm_kp_evcent,
                                             resp_norm_kp_bridging)

## view matrix
   resp_control_overlap_matrix
    
### Plot
```{r, echo=FALSE}
positions <- c(0, 0.33, 0.66, 1)
labels <- c("btwn", "evcent", "bridging", "keyplayer")
image(as.matrix(control_overlap_matrix), col=gray(32:0/32), xaxt="n", yaxt="n", 
      main="Overlaps among PCA's on raw network")
axis(1, at=positions, labels=labels)
axis(2, at=positions, labels=labels)
#image(as.matrix(cutoffs_overlap_matrix[1:3,1:3]), col=gray(32:0/32), xaxt="n", yaxt="n")
```

```{r, echo=FALSE}
positions <- c(0, 0.33, 0.66, 1)
labels <- c("btwn", "evcent", "bridging", "keyplayer")
image(as.matrix(resp_control_overlap_matrix), 
      col=gray(32:0/32), xaxt="n", yaxt="n", 
      main="Overlaps among Respondents in PCA's on raw network")
axis(1, at=positions, labels=labels)
axis(2, at=positions, labels=labels)
#image(as.matrix(cutoffs_overlap_matrix[1:3,1:3]), col=gray(32:0/32), xaxt="n", yaxt="n")
```

```{r, echo=FALSE}
## save pdf

pdf(file="overlap_in_raw_net.pdf")

par(mfrow=c(2,1))
image(as.matrix(control_overlap_matrix), col=gray(32:0/32), xaxt="n", yaxt="n", 
      main="All PCA's")
axis(1, at=positions, labels=labels)
axis(2, at=positions, labels=labels)

image(as.matrix(resp_control_overlap_matrix), 
      col=gray(32:0/32), xaxt="n", yaxt="n", 
      main="Respondents in PCA's only")
axis(1, at=positions, labels=labels)
axis(2, at=positions, labels=labels)

dev.off()

```