## visualize networks


```{r, echo=FALSE}
 
rm(list=ls())
   suppressPackageStartupMessages(library(GGally))
   suppressPackageStartupMessages(library(sna))
   suppressPackageStartupMessages(library(network))
   suppressPackageStartupMessages(library(ergm))
   suppressPackageStartupMessages(library(ggplot2))
   suppressPackageStartupMessages(library(gridExtra))

```

Networks without (i.e "control", left) and with tie imputation are shown below.

```{r, echo=FALSE, results='hide', cache=TRUE} 
  ## PLOT CONTROL NETWORK
  rm(list=ls())
  r0_net <- readRDS("../../control-net/r0-net-for-885-nodes.RDS")
  set.vertex.attribute(r0_net, "respondent", "yes", v=1:298)
  set.vertex.attribute(r0_net, "respondent", "no", v=299:network.size(r0_net))
  #ggnet2(r0_net, size=1, color="respondent")

  deg_r0_net <- degree(r0_net, gmode="graph")
  summary(deg_r0_net)
  r0_net %v% "degree" <- degree(r0_net) 
  table(r0_net %v% "respondent")

  #pdf(file="ggnet-ex.pdf")
  ggnet2(r0_net, color="respondent", size=1,
         palette = "Set2")+ggtitle("Raw Data") 
  
  ## PLOT IMPUTED NETWORK
imp_networks <- readRDS("../sim-from-ergm/imputed_10_nets_w_nodemix.RDS")

  n_to_plot <- sample(1:length(imp_networks), 1)
  imp_to_plot <- sample(imp_networks, 1)
  imp_to_plot <- imp_to_plot[[1]]
  list.vertex.attributes(imp_to_plot) 

  set.vertex.attribute(imp_to_plot, "respondent", "yes", 1:298)
  set.vertex.attribute(imp_to_plot, "respondent", "no", 299:885)
   
  ggnet2(imp_to_plot, size=1, color="respondent", 
         palette = "Set2")+ggtitle("Imputed data")

  deg_imp_to_plot <- degree(imp_to_plot, gmode="graph")
  summary(deg_imp_to_plot)
  table(imp_to_plot %v% "respondent")

  isolates_in_control <- which(deg_r0_net == 0)
  deg_imp_to_plot[isolates_in_control]
  summary(deg_imp_to_plot[isolates_in_control])
```

The degree distributions in the two networks are below.

```{r, echo=FALSE, results='hide', cache=TRUE} 
control_deg_dist <- degreedist(r0_net)
cont_degrees <- names(control_deg_dist)
cont_degrees_clean_name <- as.numeric(gsub("degree", "", 
                                           cont_degrees))
length(control_deg_dist)
control_deg_dist <- as.data.frame(control_deg_dist)
control_deg_dist <- cbind(cont_degrees_clean_name, 
                          control_deg_dist, "raw")
colnames(control_deg_dist) <- c("degrees", "frequency", "network")


imp_deg_dist <- degreedist(imp_to_plot)
imp_degrees <- names(imp_deg_dist)
imp_degrees_clean_name <- as.numeric(gsub("degree", "", imp_degrees))
length(imp_deg_dist)
imp_deg_dist <- as.data.frame(imp_deg_dist)
imp_deg_dist <- cbind(imp_degrees_clean_name, imp_deg_dist, "imputed")
colnames(imp_deg_dist) <- c("degrees", "frequency", "network")

deg_dist_data <- rbind(control_deg_dist, imp_deg_dist)


# ggplot(deg_dist_data, aes(x=degrees, 
#                           y=frequency/network.size(r0_net), 
#                           fill=network))+
#     geom_bar(position="dodge", stat="identity")+
#     ylim(0, 0.05)+
#     xlab("degrees")+ylab("proportion of nodes")

png(file="raw-and-imputed-deg-dists.Rmd")
ggplot(deg_dist_data, aes(x=degrees, 
                          #frequency/network.size(r0_net), 
                          color=network))+
    geom_freqpoly(binwidth=25)+
    #ylim(0, 0.05)+
    xlab("Degrees")+ylab("Number of nodes")
dev.off()

```

```{r, echo=FALSE, results='hide'}
  r0_net_no_isolates_ids <- which(degree(r0_net, gmode="graph") > 0)
  #r0_net_no_isolates_ids <- (r0_net %v% "vertex.names")[-c(r0_net_isolates_ids)] 
  imp_to_plot_isolates_ids <- which(degree(imp_to_plot, gmode="graph") > 0)

  r0_net_no_isolates <- get.inducedSubgraph(r0_net, v=r0_net_no_isolates_ids)

  imp_to_plot_no_isolates <- get.inducedSubgraph(imp_to_plot, v=r0_net_no_isolates_ids)
```

```{r, echo=FALSE, results='asis'}
  ggnet2(r0_net_no_isolates, color="respondent", size=1,
         palette = "Set2")+ggtitle("Raw Data (Isolates not shown)")

  ggnet2(imp_to_plot_no_isolates, color="respondent", size=1,
         palette = "Set2")+ggtitle("Imputed Data (Isolates not shown)")
```


```{r, echo=FALSE, results='asis'}
  ggnet2(r0_net_no_isolates, color="respondent", size=1,
         palette = "Set2")+ggtitle("Raw Data (Isolates not shown)")

  ggnet2(imp_to_plot_no_isolates, color="respondent", size=1,
         palette = "Set2")+ggtitle("Imputed Data (Isolates not shown)")
```

```{r, echo=FALSE, results='asis'}

raw_p <- ggnet2(r0_net_no_isolates, color="respondent", size=1,
            palette = "Set2")+ggtitle("Raw Data")

imp_p <- ggnet2(imp_to_plot_no_isolates, color="respondent", size=1,
            palette = "Set2")+ggtitle("Imputed Data")

pdf(file="nets_2row.pdf")
grid.arrange(raw_p, imp_p, nrow=2)
dev.off()

```{r, echo=FALSE, results='asis'}
### degree distributions of respondents and nonrespondents
### in the raw and imputed networks

## raw network
r0_net_degrees <- degree(r0_net, gmode="graph")
r0_net_degrees_respondents <- r0_net_degrees[1:298]
r0_net_degrees_nonrespondents <- r0_net_degrees[299:length(r0_net_degrees)]

## selected imputed network
imp_net_degrees <- degree(imp_to_plot, gmode="graph")
imp_net_degrees_respondents <- imp_net_degrees[1:298]
imp_net_degrees_nonrespondents <- imp_net_degrees[299:length(imp_net_degrees)]

## respondent data on raw and imputed network
resp_deg_dist_data <- as.data.frame(c(r0_net_degrees_respondents, 
                                      imp_net_degrees_respondents))
resp_deg_dist_data_df <- as.data.frame(resp_deg_dist_data)
resp_deg_dist_data_df[,2] <- c(rep("raw", 298), rep("imputed", 298))                                                           
colnames(resp_deg_dist_data_df) <- c("frequency", "network")

resp_deg_dist_data_df$network <- as.factor(resp_deg_dist_data_df$network)
levels(resp_deg_dist_data_df$network) <- rev(levels(resp_deg_dist_data_df$network))

## nonrespondent data on raw and imputed networks
nonresp_deg_dist_data <- as.data.frame(c(r0_net_degrees_nonrespondents, 
                                      imp_net_degrees_nonrespondents))
nonresp_deg_dist_data_df <- as.data.frame(nonresp_deg_dist_data)
nonresp_deg_dist_data_df[,2] <- c(rep("raw", 587), rep("imputed", 587))                                                           
colnames(nonresp_deg_dist_data_df) <- c("frequency", "network")

nonresp_deg_dist_data_df$network <- as.factor(nonresp_deg_dist_data_df$network)
levels(nonresp_deg_dist_data_df$network) <- rev(levels(nonresp_deg_dist_data_df$network))

p_resp_deg_dist <- ggplot(resp_deg_dist_data_df, 
                       aes(x=frequency,  
                           color=network))+
                      geom_freqpoly(binwidth=10)+
                      xlab("Degrees")+ylab("Number of nodes")+
  scale_x_continuous(breaks=(seq(0, 1200, by=100)))+
  ggtitle("Degree Distribution for Respondents")

p_nonresp_deg_dist <- ggplot(nonresp_deg_dist_data_df, 
                             aes(x=frequency,  
                                 color=network))+
                             geom_freqpoly(binwidth=10)+
                             xlab("Degrees")+ylab("Number of nodes")+
  scale_x_continuous(breaks=(seq(0, 1200, by=100)))+
  ggtitle("Degree Distribution for Nonrespondents")

png(file="raw_and_imputed_deg_dist.png")
grid.arrange(p_resp_deg_dist, p_nonresp_deg_dist, nrow=2)
dev.off()

```
```{r}
save.image(file="data_to_plot_nets.RData")
```